---
title: "Linear models"
output: github_document
date: "2022-11-10"
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)

```

Load NYC Airbnb data.
```{r, include=FALSE}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit the first model
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) + geom_point()
```

```{r}
fit = lm(price~stars+borough,data=nyc_airbnb)


```
Let's look at the result
```{r}
fit

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

Let's look at the result better
```{r, include = FALSE}
broom::glance(fit)

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable(digits = 2)
```

Let's change reference category

```{r}
fit = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough)) %>% 
      lm(price ~ stars+borough, data = .)
  

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")) %>% 
      select(term, estimate, p.value) %>% 
      knitr::kable(digits = 2)

fit %>% 
  broom::glance() %>% 
  select(AIC)
```

## Diagnostics

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin() + 
  ylim(-250, 250)


modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point() + 
  facet_wrap(.~borough)
```

## Hypothesis testing
This does t-test by default
```{r}
fit %>% 
  broom::tidy()
```

What about the significance of 'borough'.

```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)

fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```


## Nest data, fit models
This is pretty formal and also complex
```{r}
fit = lm(price ~ stars*borough + room_type*borough, data = nyc_airbnb)

broom::tidy(fit)
```

## Room type by borough
Interactions...?

```{r}
fit = nyc_airbnb %>% 
  lm(price ~ stars + borough*room_type, data=.)

fit %>% 
  broom::tidy()
```

This is more exploratory but maybe easier to understand
```{r}
nyc_airbnb %>% 
  nest(df = -borough) %>% 
  mutate(
    models = map(.x = df, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(borough,results) %>% 
  unnest(results) %>% 
  filter(term == "stars")


nyc_airbnb %>% 
  nest(df = -borough) %>% 
  mutate(
    models = map(.x = df, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(borough,results) %>% 
  unnest(results) %>% 
  filter(term != "(Intercept)") %>% 
  select(borough, term, estimate) %>% 
  pivot_wider(
    names_from = borough,
    values_from = estimate
  )
  
```

Quick double check ...?

```{r}
nyc_airbnb %>% 
  filter(borough == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Let's nest even more...
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data,-models) %>% 
  unnest(results) %>% 
  filter(str_detect(term,"room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate))+
  geom_point()+
  facet_wrap(. ~term)+
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 1))
```

